Make any stupid plot you want

### 2020-09-25 draft/intro.tex
finish out math + tables

Steven's defines the group

>>>>

Steven's identifies the group symmetries for the measurement scales\cite{stevensTheoryScalesMeasurement1946} as follows:

\begin{table}
    \begin{tabular}{l l l l}
        nominal & permutation group & one to one substitutions & $=, \neq $\\
        ordinal & isotonic group & monotonic increasing functions & $\leq, \geq$\\
        interval & general linear group & & $+, -$, matrix multiplication\\
        ratio & similarity group & & \\
    \end{tabular}
\end{table}
